%-------------------------
% Resume in Latex
% Author : Marcos Nikel
% Tailored for Design Engineer
%------------------------

\documentclass[letterpaper,10.5pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.2in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{2pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Custom commands
\newcommand{\resumeItem}[1]{\item[$\bullet$] \small{{#1 \vspace{-3pt}}}}
\newcommand{\resumeSubheading}[4]{
  \vspace{4pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[topsep=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Marcos Nikel} \\ \vspace{1pt}
    \small\href{mailto:marcosnikeldev@gmail.com}{\underline{marcosnikeldev@gmail.com}} $|$
    \href{https://linkedin.com/in/mnikel}{\underline{linkedin.com/in/mnikel}} $|$
    \href{https://github.com/marcossnikel}{\underline{github.com/marcossnikel}} \\
\end{center}

%-----------SUMMARY-----------
\section{Summary}
\resumeSubHeadingListStart
\item \small Software Engineer who started in frontend, grew into full-stack, and is now gravitating back to design and user experience. I care about how interfaces feel, not just how they work. Experienced with React, TypeScript, Next.js, and building products where the details matter.
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Software Engineer}{Jan 2026 -- Present}
{Salsa}{Remote}
\resumeItemListStart
\resumeItem{Built the end-to-end UI and backend for US tax filings across all states, serving 100K+ workers. Designed a clear interface for the compliance team to select employers, review filing data, and run submissions in batches.}
\resumeItem{Collaborated with a designer from scratch on an audit system to track all changes within the platform. Worked through information density, filters, and human-readable descriptions, reducing CX friction by over 50\%.}
\resumeItem{Implemented a proactive validation system that catches filing issues before they happen and alerts via Slack in real time, avoiding surprises with tax deadlines.}
\resumeItemListEnd

\resumeSubheading
{Software Engineer}{Sep 2024 -- Jan 2026}
{Mercado Libre}{S\~ao Paulo, Brazil}
\resumeItemListStart
\resumeItem{Led the frontend implementation of a full i18n system, building React components and Node.js services for multi-region accessibility.}
\resumeItem{Built and maintained React interfaces with TypeScript, focusing on type safety, responsive design, and cross-browser consistency.}
\resumeItem{Optimized high-traffic Node.js/Golang services handling 500K RPM, reducing API response times by 20ms.}
\resumeItemListEnd

\resumeSubheading
{Software Engineer}{Dec 2023 -- Aug 2024}
{NowCM}{Luxembourg, Remote}
\resumeItemListStart
\resumeItem{Built full-stack web applications using React with TypeScript and Node.js APIs.}
\resumeItem{Improved frontend performance with lazy loading and code splitting, reducing page load times by 40\%.}
\resumeItem{Designed and implemented RESTful APIs with authentication and validation for production applications.}
\resumeItemListEnd

\resumeSubheading
{Software Engineer}{Jun 2022 -- Dec 2023}
{Minutrade}{S\~ao Paulo, Brazil}
\resumeItemListStart
\resumeItem{Developed React dashboards with real-time data visualization for internal teams.}
\resumeItem{Created a reusable React component library with a consistent design system used across multiple projects.}
\resumeItem{Built scalable Node.js APIs with caching and integrated AWS S3 for seamless file management experiences.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{BSc Computer Science}{Feb 2022 -- Jun 2025}
{Anhembi Morumbi University}{S\~ao Paulo, Brazil}
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\resumeSubHeadingListStart
\item \small \textbf{Frontend}: React, TypeScript, Next.js, Tailwind CSS, HTML/CSS, Figma
\item \small \textbf{Backend}: Node.js, Golang, RESTful APIs, PostgreSQL, MongoDB, Redis
\item \small \textbf{Cloud/DevOps}: AWS, GCP, Docker, Kubernetes, CI/CD, GitHub Actions
\resumeSubHeadingListEnd

%-----------LANGUAGES-----------
\section{Languages}
\resumeSubHeadingListStart
\item \small English (C1) $|$ Portuguese (Native) $|$ Spanish (Intermediate)
\resumeSubHeadingListEnd

\end{document}
